### 2018-10-05 paper/conclusion.tex
Fixed a few typos

In 
\fixme{From the proofs of the main theorems, and what you say below, I
thought you did have verdicts coming from deadlock, and you simply chose not
to mark it with an inc event.} 
contrast to that, our test cases specified in
Section~\ref{sec:finitecompletefails} and \ref{sec:finitecomplete} are
adaptive. This has the advantage that test executions $(Q\parallel[\Sigma]
U_F(p))$ for failures refinement never block before the final step specified
by branch (\ref{eq:ufd}), and so we do not need inconclusive test results.
It should be noted, however, that it is
necessary for our test verdicts to recognise also deadlocks in the final test
step and interpret them as FAIL, as described in
Section~\ref{sec:finitecompletefails}. In practice, this is realised by
adding a timeout event to the testing environment which indicates deadlock
situations. For real-time systems, this is an accepted technique, because the
SUT has to respond within a pre-defined latency interval, otherwise its
behaviour is considered to be blocked and regarded as a failure.
The tests executions $(Q\parallel[\Sigma] U_T(p))$ 
\fixme{Missing hiding.}
\fxnote{jp: Here, the hiding operator is not necessary: the possible test executions are really the traces of $Q$ parallel $U_T(p)$. The hiding is only needed to specify the verdict.}  
for trace refinement never
block at all before stopping after the verdict $\epass$ or $\efail$, unless the
SUT process $Q$ has an unexpected deadlock state. 
\fxfatal{And also, if the SUT blocks, the test should block,
no?}\fxnote{jp: you are right, I changed the text here and added explanations above after the verdict explanation
in formula (\ref{eq:passT}).}
Recall from the explanations given in Section~\ref{sec:finitecomplete} that the 
blocking situation also leads to passing the test, because 
$(\epass\then \Stop)\lessdet_T (Q\parallel[\Sigma] U_T(p))\hide\Sigma$ still holds
if $(Q\parallel[\Sigma] U_T(p))\hide\Sigma$ only produces the empty trace.

The adaptive behaviour of both our test case types $U_F(p)$ and $U_T(p)$,
however, induces the obligation to check that {\it all}
possible executions have been
performed before the test can be considered as passed. Typically, it is
therefore assumed that a \emph{complete testing
assumption}~\cite{hierons_testing_2004} \fixme{I think you need this for the
failures refinement tests as well.}\fxnote{jp: yes, I re-arranged the text accordingly.} holds, which means that every possible
behaviour of the SUT is performed after a finite number of test executions.
In practice, this is realised by executing each test several times, recording
the traces that have been performed, and using hardware or software coverage
analysers to determine whether all possible test execution behaviours of the
SUT have been observed. Therefore, adaptive test cases come at the price of
having to apply some grey-box testing techniques enabling us to decide
whether all SUT behaviours have been observed.

@@

% ==============================================================================
\subsubsection*{Implications for CSP Model Checking}
As explained in the previous sections, passing a test is specified by
$(\epass\then\Stop) \lessdet_F (Q\parallel[\Sigma] U(F(j)) \hide \Sigma$ for
failures testing. If the SUT $Q$ is not a programmed piece of software or an
integrated hardware or software system, but just another CSP process
specification, it is of course possible to verify the pass criterion using
the FDR4 model checker. For checking the refinement relation $P\lessdet_F Q$,
the pass criterion has to be verified for $j=0,\dots,pq-1$, where $p$ and $q$
indicate the number of nodes in $P$'s transition graph and the maximal number
of nodes in $Q$'s graph, respectively (Theorem~\ref{th:failurestest}). Since
the test cases $U(F(j)$ have such a simple structure, it is an interesting
question for further research whether checking $(\epass\then\Stop) \lessdet_F
(Q\parallel[\Sigma] U(F(j)) \hide \Sigma$ for $j=0,\dots,pq-1$ can be faster
than directly checking $P\lessdet_F Q$, as one would do in the usual approach
with FDR4. This is of particular interest, since the checks could be
parallelised on several CPUs. Alternatively it is interesting to investigate
whether the check\footnote{We are grateful to Bill Roscoe for suggesting this
option.}
\[
(\epass\then\Stop) \lessdet_F (Q\parallel[\Sigma] \Intchoice_{j=0}^{pq-1} U_F(j)) \hide \Sigma
\]
may perform better than the check of $P\lessdet_F Q$, since the former allows for
other optimisations in the model checker than the latter.

>>>>

In 
\fixme{From the proofs of the main theorems, and what you say below, I
thought you did have verdicts coming from deadlock, and you simply chose not
to mark it with an inc event.} 
contrast to that, our test cases specified in
Section~\ref{sec:finitecompletefails} and \ref{sec:finitecomplete} are
adaptive. This has the advantage that test executions $(Q\parallel[\Sigma]
U_F(j))$ for failures refinement never block before the final step specified
by branch (\ref{eq:ufd}), and so we do not need inconclusive test results.
It should be noted, however, that it is
necessary for our test verdicts to recognise also deadlocks in the final test
step and interpret them as FAIL, as described in
Section~\ref{sec:finitecompletefails}. In practice, this is realised by
adding a timeout event to the testing environment which indicates deadlock
situations. For real-time systems, this is an accepted technique, because the
SUT has to respond within a pre-defined latency interval, otherwise its
behaviour is considered to be blocked and regarded as a failure.
The tests executions $(Q\parallel[\Sigma] U_T(j))$ 
\fixme{Missing hiding.}
\fxnote{jp: Here, the hiding operator is not necessary: the possible test executions are really the traces of $Q$ parallel $U_T(j)$. The hiding is only needed to specify the verdict.}  
for trace refinement never
block at all before stopping after the verdict $\epass$ or $\efail$, unless the
SUT process $Q$ has an unexpected deadlock state. 
\fxfatal{And also, if the SUT blocks, the test should block,
no?}\fxnote{jp: you are right, I changed the text here and added explanations above after the verdict explanation
in formula (\ref{eq:passT}).}
Recall from the explanations given in Section~\ref{sec:finitecomplete} that the 
blocking situation also leads to passing the test, because 
$(\epass\then \Stop)\lessdet_T (Q\parallel[\Sigma] U_T(j))\hide\Sigma$ still holds
if $(Q\parallel[\Sigma] U_T(j))\hide\Sigma$ only produces the empty trace.

The adaptive behaviour of both our test case types $U_F(j)$ and $U_T(j)$,
however, induces the obligation to check that {\it all}
possible executions have been
performed before the test can be considered as passed. Typically, it is
therefore assumed that a \emph{complete testing
assumption}~\cite{hierons_testing_2004} \fixme{I think you need this for the
failures refinement tests as well.}\fxnote{jp: yes, I re-arranged the text accordingly.} holds, which means that every possible
behaviour of the SUT is performed after a finite number of test executions.
In practice, this is realised by executing each test several times, recording
the traces that have been performed, and using hardware or software coverage
analysers to determine whether all possible test execution behaviours of the
SUT have been observed. Therefore, adaptive test cases come at the price of
having to apply some grey-box testing techniques enabling us to decide
whether all SUT behaviours have been observed.

@@

% ==============================================================================
\subsubsection*{Implications for CSP Model Checking}
As explained in the previous sections, passing a test is specified by
$(\epass\then\Stop) \lessdet_F (Q\parallel[\Sigma] U_F(j)) \hide \Sigma$ for
failures testing. If the SUT $Q$ is not a programmed piece of software or an
integrated hardware or software system, but just another CSP process
specification, it is of course possible to verify the pass criterion using
the FDR4 model checker. For checking the refinement relation $P\lessdet_F Q$,
the pass criterion has to be verified for $j=0,\dots,pq-1$, where $p$ and $q$
indicate the number of nodes in $P$'s transition graph and the maximal number
of nodes in $Q$'s graph, respectively (Theorem~\ref{th:failurestest}). Since
the test cases $U_F(j)$ have such a simple structure, it is an interesting
question for further research whether checking $(\epass\then\Stop) \lessdet_F
(Q\parallel[\Sigma] U_F(j)) \hide \Sigma$ for $j=0,\dots,pq-1$ can be faster
than directly checking $P\lessdet_F Q$, as one would do in the usual approach
with FDR4. This is of particular interest, since the checks could be
parallelised on several CPUs. Alternatively it is interesting to investigate
whether the check\footnote{We are grateful to Bill Roscoe for suggesting this
option.}
\[
(\epass\then\Stop) \lessdet_F (Q\parallel[\Sigma] \Intchoice_{j=0}^{pq-1} U_F(j)) \hide \Sigma
\]
may perform better than the check of $P\lessdet_F Q$, since the former allows for
other optimisations in the model checker than the latter.
